%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{caption}
%\DeclareCaptionType{copyrightbox}
%\graphicspath{{./figures/}}
\usepackage{subcaption}
\usepackage{url}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{amsmath, amsfonts, amssymb}
\graphicspath{{./figures/}}
\usepackage{color}
%package for proper unicode rendering
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\setlength{\titlebox}{2.8in}
\inputencoding{utf8}

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}  
 \begin{document}
\newcommand{\narenc}[1]{[{\color{red} Naren writes: \it #1}]}
\newcommand{\sathappanc}[1]{[{\color{blue} Sathappan writes: \it #1}]}
\newcommand{\then}{\Rightarrow}
\newcommand{\softor}{\operatornamewithlimits{\tilde{\vee}}}
\newcommand{\softand}{\operatornamewithlimits{\tilde{\wedge}}}
\newcommand{\softthen}{\operatornamewithlimits{\tilde{\then}}}
\newcommand{\softneg}{\operatornamewithlimits{\tilde{\neg}}}
\title{Forecasting Protests \\by Detecting Future Time Mentions \\in News and Social Media}
\author{
% 1st. author
Sathappan Muthiah\\
Virginia Tech\\
Arlington, VA 22203\\
sathap1@cs.vt.edu
% 2nd. author
\And
Bert Huang\\
       University of Maryland\\
       College Park, MD 20742\\
       bert@cs.umd.edu
%% 3rd. author
       \And
Jaime Arredondo\\
       University of California\\
       San Diego, CA 92093\\
       jarredon@ucsd.edu
\AND 
% use '\and' if you need 'another row' of author names
%% 4th. author
David Mares\\
       University of California\\
       San Diego, CA 92093\\
       dmares@ucsd.edu
%% 5th. author
       \And
Lise Getoor\\
       University of California\\
       Santa Cruz, CA 95064\\
       getoor@soe.ucsc.edu
%% 6th. author
       \And
Graham Katz\\
       CACI Inc.\\
       Lanham, MD 20706\\
       ekatz@caci.com
%\AND
       \And
%% 7th. author
Naren Ramakrishnan\\
       Virginia Tech\\
       Arlington, VA 22203\\
       naren@cs.vt.edu
}
\maketitle
\begin{abstract}
\begin{quote}
\input{sections/abstract.tex}
\end{quote}
\end{abstract}
\vspace{-1em}
\label{intro}
\input{sections/introduction}

\vspace{-1em}
\section{Related Work}
\input{sections/related_works}

\vspace{-1em}
\section{Probabilistic Soft Logic}
\input{sections/psl}
\label{section:PSL}

\vspace{-1em}
\section{Approach}
\input{sections/approach}

\vspace{-1em}
\section{Experiments}
\input{sections/experiments}

\vspace{-1em}
\section{Development and Maintenance}
The core algorithms behind the
planned protest detector were implemented in Python. The PSL geocoder was
implemented in Java. The Basis Rosette Linguistic Platform is the key
external library utilized. The development process took 3 months (June
2012 to Aug 2012) and was
primarily led by the first author with contributions from the other authors.
After two months of testing (Sep 2012 and Oct 2012), the system was deployed
in Nov 2012. Since there is not an explicit training
phase, the system has required minimal re-engineering over time. Key changes
made to the system over time was to increase the sources used for data ingest
and supporting the inclusion of additional phrases. Agile software
engineering methods were used for project management.

\vspace{-1em}
\section{Discussion}
We have described an approach to forecasting protests by detecting mentions of future events in news and social
media. The two twin issues of i) resolving the date and ii) resolving the location have been addressed satisfactorily
to realize an effective protest forecasting system. As different forms of communication media gain usage, systems
like ours will be crucial to understanding the concerns of citizenry.

Our future work is aimed at three aspects. First, to address situations such as nationwide protests and systems of protests,
we must generalize our system from generating protests at a single article level to digesting groups of articles. This will
require more sophisticated reasoning using PSL programs. 
Second, we would like to generalize our approach that currently
does detection of overt plans for protest to not-so-explicitly stated expressions of discontent. 
Finally, we plan to consider other population-level events of interest than just civil unrest, e.g., domestic political crises,
and design detectors to recognize the imminence of such events.

\vspace{-0.8em}
{\small
\section*{Acknowledgments}
Supported by the Intelligence Advanced Research Projects Activity (IARPA) via
DoI/NBC contract number D12PC000337, the US Government is authorized to reproduce and distribute reprints of
this work for Governmental purposes notwithstanding any copyright annotation thereon.
Disclaimer: The views and conclusions contained herein are those of the authors and should not be interpreted as necessarily representing the official policies or endorsements, either expressed or implied, of IARPA, DoI/NBC, or the US Government.
}\vspace{-1em}
\small
\bibliographystyle{aaai}
\bibliography{references}
\end{document}
